---
title: "Effect of visual interference on visual knowledge"
author: "Pierce Edmiston"
output:
  html_document:
    theme: flatly
    toc: true
---

```{r, config, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.path = "figs/",
  cache.path = ".cache/"
)

read_chunk("knowledge_type.R")
```

```{r, setup}
```

```{r, data}
```

# Results

```{r, error-mods, echo = 1, cache = TRUE}
```

```{r, error-mods-results, cache = TRUE}
error_rate <- function(x) {
  to_pct <- function(y) y * 100
  mean(x, na.rm = TRUE) %>%
    to_pct %>%
    round(digits = 1) %>%
    paste0("%")
}
means <- question_first %>%
  group_by(feat_type, mask_type) %>%
  summarize(error = error_rate(is_error)) %>%
  spread(mask_type, error)
means

results <- list(
  feat_type = report_glmer_effect(feat_type_mod, "feat_c"),
  vis_mask = report_glmer_effect(vis_mask_mod, "mask_c"),
  non_mask = report_glmer_effect(non_mask_mod, "mask_c"),
  interaction = report_glmer_effect(error_mod, "feat_c:mask_c")
)

tidy(error_mod, effects = "fixed")
```

Without visual interference, participants were just as likely to make an error on visual questions as they were on nonvisual questions, `r results["feat_type"]`. With visual interference, errors became significantly more likely on visual questions, `r results["vis_mask"]`, but not on nonvisual questions, `r results["non_mask"]`, resulting in a marginal _interference x question type_ interaction, `r results["interaction"]`.

```{r, error-plot}
```

```{r, error-by-exp}
```

# RTs

```{r, rt-mod, echo = 1, cache = TRUE}
```

```{r}
tidy(rt_mod, effects = "fixed")
```

```{r, rt-plot}
```