---
title: "Differences among propositions"
author: "Pierce Edmiston"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: true
---

```{r, config, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.path = "propositions-figs/"
)
read_chunk("propositions.R")
```

```{r, setup}
```

```{r, data, echo = TRUE}
```

# Normative agreement

Ideally, the majority of people would agree on the truth or falseness of each of
the 536 propositions we created for this experiment, yet against our best 
intentions, there were some propositions for which people did not agree.

To determine which propositions were ambiguous, I fit a linear model to the
responses for each proposition given in the norming study. In the norming
study, participants were asked to answer the yes or no question on a
5-point scale from _Definitely no_ to _Definitely yes_. The scale was centered
on _Maybe_, corresponding to a truth value of 0. The linear models predicted
mean truth value for each proposition, and the statistical test of interest
was whether this value differently reliably from 0 (the intercept term),
which would indicate that people tended to agree on the truth or falseness
of each of the propositions.

Any proposition for which mean truth value did not significantly differ from 0
(_p_ < 0.05) was deemed "ambiguous". If the truth value of the proposition is
ambiguous as determined by the norming participants, then supposedly incorrect
responses to these propositions in the main experiment cannot be interpreted as
errors in the actual experiment.

```{r, truth-agreement}
```

```{r, save-ambiguous, echo = TRUE}
```

# Incorrectly coded propositions

With the agreement scores above, we can also check whether the correct response
as coded in the experiment matches what the norming participants thought was
the correct answer. Basically, if there are any cases that the correct response
was not the same as the norm truth value, we would conclude that these 
propositions were miscoded.

Fortunately of the questions that were not ambiguous, all of the questions
were correctly coded.

```{r, incorrect-code}
```