---
title: "Why is the distribution of by-subject effects discontinuous?"
author: "Pierce Edmiston"
output:
  html_document:
    theme: flatly
    toc: true
---

```{r, config, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 4,
  fig.height = 4
)
read_chunk("errors.R")
```

```{r, setup}
```

# Data

```{r, data}
```

# The distribution of by-subject effects

Why isn't the distribution of by-subject effects more continuous?

```{r, subj-mods}
```

## Label peaks

```{r, group-subjects}
```

# Error counts

The most likely explanation for the strange model fits is that some subjects didn't make errors in some of the cells used in the feat\_c x mask\_c model.

Here is a plot of the number of errors (count) made by subjects in each group.

```{r, error-counts, fig.width = 10, fig.height = 4}
```

# glmer

A hierarchical model should be able to account for this sparseness,
and we should expect the distribution of by-subject effects to be
more continuous.

```{r, glmer-mod, cache = TRUE}
```

```{r, glmer-density}
```

# The distribution of by-proposition mask effects

The distribution of by-proposition mask effects is discontinuous as well.

```{r, prop-mods}
```

```{r, glmer-prop-mod, cache = TRUE}
```

```{r, glmer-prop-density}
```