---
title: "The effect of visual interference on continuous measures of visual knowledge"
author: "Pierce Edmiston"
output:
  word_document: null
  html_document:
    theme: flatly
    toc: true
---

```{r, config, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  comment = NA
)
```

```{r, loaders}
read_chunk("amount_of_knowledge.R")
```

```{r, setup}
```

# Data

```{r, data, echo = TRUE}
```

# Amount of visual knowledge

```{r, imagery-mod, echo = TRUE, cache = TRUE}
```

```{r}
tidy(imagery_mod, effects = "fixed")
```

```{r, amount-of-visual}
```

## By experiment

```{r, amount-of-visual-by-exp, fig.height = 10}
```

## Outlier propositions had high imagery scores

Why isn't the effect visible in the original experiment? Because
outlier propositions had higher imagery scores, and without
propositions with high imagery scores, the range of the norming
data is too narrow.

```{r, cor}
```

```{r, data}
# HACK!!! Load the data again because `cor` chunk clobbers namespace
```

## Reanalyze with outlier propositions

```{r, imagery-mod-all, echo = TRUE, cache = TRUE}
```

```{r}
tidy(imagery_mod_all, effects = "fixed")
```

```{r, amount-of-visual-all-props}
```

```{r, amount-of-visual-all-props-by-exp, fig.height = 10}
```

# Amount of encyclopedic knowledge

```{r, facts-mod, echo = TRUE, cache = TRUE}
```

```{r}
tidy(facts_mod, effects = "fixed")
```

```{r, amount-of-nonvisual}
```

```{r, amount-of-nonvisual-by-exp, fig.height = 10}
```
